---
title: "README"
author: "Roxanne Ready"
date: "11/6/2019"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
# Setup Knitr to display code output by default but suppress messages
knitr::opts_chunk$set(echo = TRUE, paged.print = TRUE, message = FALSE)
```

```{r echo=FALSE, results='hide'}

# Function
library(tidyverse)

# Form
library(knitr)
library(kableExtra)

```

# Homelessness Across the U.S.

Data work for UMD's Howard Center for Investigative Journalism, fall 2019.

*Created by Roxanne Ready (<http://roxanneready.com>)*

*Reporter: Roxanne Ready*

## Project goal

This work was completed for UMD's Howard Center for Investigative Journalism as part of a large, collaborative project about the criminalization of homelessness in Baltimore and across the U.S.

## Project notes

### Staff involved

* Kathy Best, Howard Center Director
* Marty Kaiser, Howard Distinguished Visiting Fellow
* Sean Mussenden, Data Bureau Chief
* Deb Nelson, project lead
* Roxanne Ready, data journalist
* Theresa Diffendal, data journalist
* Investigative journalism class, fall 2019

### Data sources

```{r echo=FALSE}

tribble(
  ~Data, ~Source, ~URL,
  "Point in Time (PIT) homelessness count", "Dept. of Housing and Development", "https://www.hudexchange.info/programs/coc/coc-homeless-populations-and-subpopulations-reports/",
  "Community of Care (CoC) cluster analysis", "Zillow", "https://www.zillow.com/research/data/",
  "CoC-to-tract crosswalk", "Tom Byrne", "https://github.com/tomhbyrne/HUD-CoC-Geography-Crosswalk",
  "Maryland court data", "scraped by CNS", "http://casesearch.courts.state.md.us/casesearch/"
) %>%
  kable(format="markdown")

```

## Technical

*TK: Instructions on how to bootstrap project, run ETL processes, etc.*

An outline of the basic project structure is available at https://github.com/associatedpress/cookiecutter-r-project

### Project setup instructions

After cloning the git repo:

Open `homelessness-across-us.Rproj` in RStudio.

## Data notes

*Add important caveats, limitations, and source contact info here.*
